---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ihpdr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ihpdr)](https://CRAN.R-project.org/package=ihpdr)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/kvasilopoulos/ihpdr.svg?branch=master)](https://travis-ci.org/kvasilopoulos/ihpdr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kvasilopoulos/ihpdr?branch=master&svg=true)](https://ci.appveyor.com/project/kvasilopoulos/ihpdr)
<!-- badges: end -->

The goal of {ihpdr} is to fetch data from the [International Hous Price Database](https://www.dallasfed.org/institute/houseprice#tab1), compiled 
by the Federal Reserve Bank of Dallas.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/ihpdr")
```
## Example

This is a basic example which shows you how to download the data:

```{r example}
library(ihpdr)

# House Prices
download_raw()

# Exuberance Indicators ~ gsadf
download_exuber()

# Exuberance Indicators ~ bsadf
download_exuber("bsadf")

# Get the release dates
ihpdr::release_dates()
```

---

Please note that the 'ihpdr' project is released with a
  [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
